Recruiting Chapter

### 2020-10-26 manuscript.Rmd
draft changes

@@

<!--
As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la
 fig.cap="2-mode plot of visits by private colleges and universities", 
-->

```{r plot_g_2mode_privu, echo=FALSE, out.width = '100%'}
knitr::include_graphics("assets/figures/plot_g_2mode_privu.pdf")
```
As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la

>>>>

Figure \@ref(fig:two-mode-plot) shows a plot of the two-mode network, with private high schools vertices the color salmon, public research universities shown in violet, and private colleges and universities shown in green green. The graph layout places vertices closer together if they are similar to one another in terms of network structure. [SAY WHAT THIS MEANS, DRAWING FROM NOTES FROM RUSS].  Figure \@ref(fig:two-mode-plot) suggests that the recruiting visit patterns of private colleges and universities tend to be more similar to one another than they are to those of public research universities. By contrast, many public research universities are far away from one another and a subset of public researchg universities appear to have network structure similar to many of the private colleges and universities (e.g., CU Boulder, UC Berkeley, University of South Carolina )

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
```

@@

Figure \@ref(fig:two-mode-plot-privu) shows a plot of the two-mode network of private colleges and universities

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```

INSERT COMMUNITY DETECTION
